Towards atomistic resolution structure of phosphatidylcholine headgroup and glycerol backbone at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-10-12 HGmodelMANUSCRIPT/REPLYtoREVIEWER2.txt

The original reviewer comments are not written in this publicly available
file we do not have permission to publish those. The original comments
will be added to the version which will be submitted to the JPCB.

@@

2.
Author reply:

All the "subjective sweet spots" in Fig. 2 have exactly the same size: 0.04 units.

This size was agreed on based on the high experimental repeatibility of the order
parameters that we discuss in the text (p12): "Almost all the reported values are
within a variation of ±0.02 [...] for all fully hydrated PC bilayers, regardless
of variation in their acyl chain composition and temperature."

To make the definition of the sweet spots clear to the reader, we now explicitly
point this out when introcuding them in the text (p15):

"Motivated by the high experimental reproducibility, we have highlighted in Fig. 2
subjective sweet spots (light blue areas **spanning 0.04 units around the average
of the extremal experimental values**), within which
we expect the calculated values of the order parameters of a well-performing
force field to fall."

### 2015-10-12 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex
Update text and reply related to the issue https://github.com/NMRLipids/nmrlipids.blogspot.fi/issues/66

In general there is a good agreement between the order parameters measured with different experimental NMR techniques: Almost all the 
reported values are within a variation of $\pm$0.02 (which is also the error estimate given by Gross et al.~\cite{gross97}) 
for all fully hydrated PC bilayers, regardless of variation in their acyl chain composition and temperature.
Exceptions are the somewhat lower order parameters reported from some measurements using $^1$H-$^{13}$C NMR~\cite{hong95a,hong95b,warschawski05}.
In these experiments, however, the reported error bars are either relatively large~\cite{hong95a,hong95b}, 
or the spectral resolution is quite low and numerical lineshape simulations have not been used in the analysis~\cite{warschawski05}.
As it, therefore, is highly likely that the reported lower order parameters are due to lower experimental 
accuracy, we exclude them from the present discussion;
for more details, see Ref.~\citenum{accuracyPOST}. 
Motivated by the high experimental reproducibility, we have highlighted in 
Fig.~\ref{HGorderparameters} subjective sweet spots (light blue areas spanning 0.04 units), within which we expect the calculated  
values of the order parameters of a well-performing force field to fall.

>>>>

In general there is a good agreement between the order parameters measured with different experimental NMR techniques: Almost all the 
reported values are within a variation of $\pm$0.02 (which is also the error estimate given by Gross et al.~\cite{gross97}) 
for all fully hydrated PC bilayers, regardless of variation in their acyl chain composition and temperature.
Exceptions are the somewhat lower order parameters reported from some measurements using $^1$H-$^{13}$C NMR~\cite{hong95a,hong95b,warschawski05}.
In these experiments, however, the reported error bars are either relatively large~\cite{hong95a,hong95b}, 
or the spectral resolution is quite low and numerical lineshape simulations have not been used in the analysis~\cite{warschawski05}.
As it, therefore, is highly likely that the reported lower order parameters are due to lower experimental 
accuracy, we exclude them from the present discussion;
for more details, see Ref.~\citenum{accuracyPOST}. 
Motivated by the high experimental reproducibility, we have highlighted in 
Fig.~\ref{HGorderparameters} subjective sweet spots (light blue areas spanning 0.04 units around the average
of the extremal experimental values), within which we expect the calculated  
values of the order parameters of a well-performing force field to fall.
